Fixing Vulnerabilities Hinders Maintainability

### 2019-02-03 paper/ICPC19/icpc19.tex
review

\textbf{\textit{Security refactorings harm the maintainability of open-source software.}}

@@

The impact of a refactoring depends on its complexity, i.e., if the refactoring adds complexity to the codebase it is probably affecting the software maintainability. One evidence of that is the fact of \emph{Cross-Site Scripting} and \emph{Using Components with Know Vulnerabilities} refactorings endure more cases without any impact in the maintainability. Typically, these type of vulnerabilities are one line fixes --- adding an \texttt{escape} function or changing the version of the component, respectively. Whereas, Broken Authentication and vulnerabilities such as the one presented in Section \ref{sec:motivation} responsible by DoS attacks are more difficult to fix (several code lines deleted and added). Another example is the Apple authentication flaw discovered in 2017 (CVE-2017-13872)\footnote{CVE-2017-13872 details available at https://support.apple.com/en-us/HT208315 (Accessed on \today{})}, where any user could login as root with an empty password. Patrick Wardle examined the cause of the issue\footnote{\emph{Why $<$blank$>$ Gets You Root} available at https://objective-see.com/blog/blog\_0x24.html (Accessed on \today{})} and conclude that the flaw was due to the introduction of high cyclomatic complexity in a method used to verify the password. In sum, \emph{Cross-Site Scripting} and \emph{Using Components with Known Vulnerabilities} should take part of the developers preocupations along with the other patterns that explicitly hinder maintainability because despite their low complexity these are patterns that still produce a considerable negative impact on the maintainability. Real efforts have been made in creating and incorporating coding standards and best practices in software production. However, security is still far from perfection and fixing vulnerabilities might hinder software maintainability. Thus, it is important to provide tool support to developers to help them applying these patterns without harming software maintainability.

\section{Threats to Validity}\label{sec:threats}
%
The following section presents the potential threats to validity of this study.
%
\subsection{Construct}
%
The maintainability formula was inferred based on the reports of the Better Code Hub.
The high amount of different projects and backgrounds may require different maintainablity
standards. However, BCH does have a representative benchmark of closed and open-source
software projects that is under the calculation of the thresholds used in the computation
of each maintainability guideline (Table \ref{tab:guidelines})~\cite{Visser:2016:OREILLY,
Baggen2012}.

@@

@@

In contrast to the BCH benchmark, this study uses a dataset that only covers open-source software to perform the maintanibility evaluation. However, BCH thresholds are calculated from a set of both open and closed sotfware. Different programming languages may require different coding practices to address software safety. The dataset
comprises more commits in C and PHP, i.e., the dataset may not be properly representative of the population regarding to programming languages.

@@

@@

@@

@@

@@

>>>>

\textbf{\textit{Security refactorings harm the maintainability of open-source software.}}
\Luis{Nao uses numeros no inico da frase. --> We found that 40.2\% of the security refactorings}

@@

The impact of a refactoring depends on its complexity, i.e., if the refactoring
adds complexity to the codebase it is probably affecting the software
maintainability. One evidence of that is the fact of \emph{Cross-Site
Scripting} and \emph{Using Components with Know Vulnerabilities} refactorings
endure more cases without any impact in the maintainability. Typically, these
type of vulnerabilities are one line fixes --- adding an \texttt{escape}
function or changing the version of the component, respectively. Whereas,
Broken Authentication and vulnerabilities such as the one presented in Section
\ref{sec:motivation} responsible by DoS attacks are more difficult to fix
(several code lines deleted and added). Another example is the Apple
authentication flaw discovered in 2017 (CVE-2017-13872)\footnote{CVE-2017-13872
details available at https://support.apple.com/en-us/HT208315 (Accessed on
\today{})}, where any user could login as root with an empty password. Patrick
Wardle examined the cause of the issue\footnote{\emph{Why $<$blank$>$ Gets You
Root} available at https://objective-see.com/blog/blog\_0x24.html (Accessed on
\today{})} and conclude that the flaw was due to the introduction of high
cyclomatic complexity in a method used to verify the password. In sum,
\emph{Cross-Site Scripting} and \emph{Using Components with Known
Vulnerabilities} should take part of the developers preoccupations along with
the other patterns that explicitly hinder maintainability because despite their
low complexity these are patterns that still produce a considerable negative
impact on the maintainability. Real efforts have been made in creating and
incorporating coding standards and best practices in software production.
However, security is still far from perfection and fixing vulnerabilities might
hinder software maintainability. Thus, it is important to provide tool support
to developers to help them applying these patterns without harming software
maintainability.

\section{Threats to Validity}\label{sec:threats}
%
The following section presents the potential threats to validity of this study.
%
\subsection{Construct}
%

\Luis{Better Code Hub -> BCH}
The maintainability formula was inferred based on the reports of the Better Code Hub.
The high amount of different projects and backgrounds may require different maintainability
standards. However, BCH does have a representative benchmark of closed and open-source
software projects that is under the calculation of the thresholds used in the computation
of each maintainability guideline (Table \ref{tab:guidelines})~\cite{Visser:2016:OREILLY,
Baggen2012}.

@@

\Luis{maintainability still may be affected -> maintainability may sitll be affected}

@@

\Luis{A primeira threat que falas é que os resultados podem nao generalizar
para software fechado. Eu acho que deviamos ser mais diretos. Para alem disso
tirava o "In contrast to the BCH benchmark,"}

In contrast to the BCH benchmark, this study uses a dataset that only covers
open-source software to perform the maintainability evaluation. However, BCH
thresholds are calculated from a set of both open and closed software.
Different programming languages may require different coding practices to
address software safety. The dataset comprises more commits in C and PHP, i.e.,
the dataset may not be properly representative of the population regarding to
programming languages.

@@

\Luis{pode ser uma cena só minha mas acho que fica melhor em vez de comecar
fraseds com "And," usar outros conetores tipo "Besides," "In addition,", etc. œ}

@@

\Luis{eu nao acho que usar 10 guidelines proposed by the Software Improvement
Group (SIG) seja algo que nos esteja a diferenciar. Acho que o a prinicpal
diferenca é que estamos a estudar maintainability issues noutro contexto.}

@@

\Luis{ tambem fizemos analise por linguagem, nesta ultima citacao deviamos falar sobre isso tb.}

@@

\luis{secure security frameworks, nao percebi bem o que se quer dizer aí.}

@@

\luis{many directions such as -> many directions:}
